SDR enhancement by clouds

### 2024-03-23 article/article.Rmd
Commit 2024-03-23 23:12

.......here.....

Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.

After some evaluation of the modeled radiation in different atmospheric conditions,
in relation to the GHI data, we choose as a representative of the clear sky radiation,
the case with
$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.

@@

<!---
Many have used models or some statistical method to determine then CE thresholds.
-->

>>>>

We evaluasted the performanse of the modeled clear radiation for the different atmospheric conditions,
as reference. 
by an empirica approach by inspecting a set of chosen days.

we adjusted teh threshold for each and chek then results

After evaluating the modeled clear radiation for the different atmospheric conditions,
in relation to the measured GHI data, we choose as a representative of the clear sky radiation,
the case with
$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.

- can folleo for clear days
- this selection has some subjectivity
- the most importand are the thresholds

Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
This selection has some subjectivity, as the definition of clear sky, is in relation
of the intended usage. Our main focus is to be able to identify the OI created by the
clouds. Although, the aerosols and water vapor are always present and can not be
completely removed. The effect of the different clearness lavels

model have to be uniform on clear days

the level is adjusted by the threshold

the effect of the sza uniform

@@
